Choosing a Population Genomics Approach

### 2022-02-04 RADseq.Rmd
fixed overlap of navbar, some radseq edits

1) [Look at your raw data.](#fastqc)
2) [Run an assembly pipeline](#assembly) through to a SNP dataset, using either all samples or a representative subset. Parameters can come from those used in a similar study, or default parameters.
3) Filter your data minimally, then [evaluate for potential sources of error.](#error)
4) Subset or remove individuals based on initial evaluation.  
5) Using a representative subset of samples, [test key parameters](#test) to optimize your assembly.
6) Run your optimized assembly on all non-removed samples.
7) Evaluate the difference between multiple filtering schemes for your analyses of interest. *Popgen analysis guide coming soon*
8) Repeat as needed.

1) [Look at your raw data.](#fastqc)
2) [Run an assembly pipeline](#assembly), using either all samples or a representative subset.
3) [Evaluate potential sources of error.](#error)
4) [Remove individuals based on initial evaluation](#bad).  
5) [Test a range of key parameters](#test) to optimize your assembly.
6) Run your optimized assembly on all non-removed samples.
7) [Filter your SNPs](#filter)
8) Repeat as needed!

## First, look at the raw data! {#fastqc}  
Always look at your data with [FastQC](https://www.bioinformatics.babraham.ac.uk/projects/fastqc/) before starting an assembly. First, this is a good check to just make sure the sequencing worked. If you have demultiplexed data, you can use [MultiQC](https://multiqc.info/) to generate FastQC plots for all individuals and quickly identify ones that did not sequence well.  
Check out [this informative tutorial](https://datacarpentry.org/wrangling-genomics/02-quality-control/index.html) on running FastQC and interpreting the output.  
**Questions to ask:** Do you have a lot of adapter sequences? Are the ends of your reads very low quality? If so, you should expect a fair amount of trimming and read filtering to occur prior to assembly. If that doesn't occur or if too many reads are being filtered so as to only recover a small number of SNPs, something might need to be tweaked with your trimming and filtering step.

@@

## Filtering SNPs {#filter}
### (and embrace the missingness!) {.unlisted .unnumbered}

@@

# Helpful tutorials  
* [Marine Genomics open course](https://baylab.github.io/MarineGenomics/)
* [UNIX tutorial](http://evomics.org/learning/unix-tutorial/)
* [what is a VCF file and how can I filter it?](http://evomics.org/learning/population-and-speciation-genomics/2020-population-and-speciation-genomics/first-steps-in-genomic-data-analysis/)

>>>>

<!-- 1) [Look at your raw data.](#fastqc)
2) [Run an assembly pipeline](#assembly) through to a SNP dataset, using either all samples or a representative subset. Parameters can come from those used in a similar study, or default parameters.
3) Filter your data minimally, then [evaluate for potential sources of error.](#error)
4) Subset or remove individuals based on initial evaluation.  
5) Using a representative subset of samples, [test key parameters](#test) to optimize your assembly.
6) Run your optimized assembly on all non-removed samples.
7) Evaluate the difference between multiple filtering schemes for your analyses of interest. *Popgen analysis guide coming soon*
8) Repeat as needed. -->

1) [Look at your raw data.](#fastqc)
2) [Run an assembly pipeline](#assembly), using either all samples or a representative subset.
3) [Evaluate potential sources of error.](#error)
4) [Remove individuals based on initial evaluation](#bad).  
5) [Test a range of key parameters](#test) to optimize your assembly.
6) Run your optimized assembly on all non-removed samples.
7) [Filter your SNPs](#filter)
8) [Repeat as needed!](#repeat)

## First, look at the raw data! {#fastqc}  
Always look at your data with [FastQC](https://www.bioinformatics.babraham.ac.uk/projects/fastqc/) before starting an assembly. First, this is a good check to just make sure the sequencing worked. If you have demultiplexed data, you can use [MultiQC](https://multiqc.info/) to generate FastQC plots for all individuals and quickly identify ones that did not sequence well.

Check out [this informative tutorial](https://datacarpentry.org/wrangling-genomics/02-quality-control/index.html) on running FastQC and interpreting the output.

**Questions to ask:** Do you have a lot of adapter sequences? Are the ends of your reads very low quality? If so, you should expect a fair amount of trimming and read filtering to occur prior to assembly. If that doesn't occur or if too many reads are being filtered so as to only recover a small number of SNPs, something might need to be tweaked with your trimming and filtering step.
<!--ADW: elaborating what you mean by 'tweaked' or possibly providing a link to some resources for how someone might thoughtfully change the parameters for their trimming and filtering steps.-->

@@

## Filtering SNPs {#filter}

### (and embrace the missingness!) {.unlisted .unnumbered}

@@

## Repeat as needed {#repeat}
# Helpful tutorials  
* [Marine Genomics open course](https://baylab.github.io/MarineGenomics/)
* [UNIX tutorial](http://evomics.org/learning/unix-tutorial/)
* [what is a VCF file and how can I filter it?](http://evomics.org/learning/population-and-speciation-genomics/2020-population-and-speciation-genomics/first-steps-in-genomic-data-analysis/)

### 2022-02-04 choosing-population-genetics.Rmd
fixed overlap of navbar, some radseq edits

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html",
             hyperlink = "to.doc")
```

>>>>

```{r setup, include=FALSE}
#library(knitr)
knitr::opts_chunk$set(echo = TRUE)
library(knitcitations)
library(kableExtra)
opts_chunk$set(fig.width = 10,
               fig.height = 5,
               cache = FALSE)
cite_options(citation_format = "pandoc", max.names = 3, style = "html",
             hyperlink = "to.doc")
```
